Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
worked on early secs of paper

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization
  is a long-standing challenging area in biology.
  To understand how hydrodynamic flow may be used to actively
  control self-assembly of Janus particles (JPs), we use a model
  recently developed for the many-body hydrodynamics of amphiphilic
  JPs suspended in a viscous background flow (JFM, 941, 2022).
  We investigate how various bilayer structures arise from tuning
  the hydrophobic properties of the JP-solvent interface.
  Focusing on a simple tuing of the hydrophobicity distribution,
  we found
  JPs assembled into uni-lamella, multi-lamella and striated
  structures.  To introduce dynamics, we include a linear shear flow and a
  Taylor-Green mixing flow, and measure the
  collective dynamics of JP particles in terms of their 
  (a) free energy from the hydrophobic interactions between the JPs,
  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
  and (c) strain parameter that captures the deformation in the assembly.
  We characterized the effective material proporties of the JP structures
  and found that the uni-lamellar structures increases orientation order under
  shear flow, the multilamellar structure behaves as a shear thinning fluid,
  and the striated structure possesses a finite yield stress.  
  These numerical result provide insights into dynamic control of
  non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles (JPs) are colloids with two surfaces of different
properties.
For example, it is common for the surface of a Janus particle to
be partly hydrophilic and hydrophobic (polar and non-polar).
In a viscous solvent, Janus particles often self-assemble into
structures with tunable functions for biomedical engineering
applications
\cite{
  GheisariSahfieeAbbasiEtAl2021_DMR,
  LiuYangHuangEtAl2016_Angew,
  LiWangYaoEtAl2019_Nanoscale,
  Bradley2016}.
Depending on the interactions between Janus particles and the surrounding viscous solvent,
JPs self-assemble into oligomers of various geometries and sizes\cite{Bradley2017}.

Dynamics offers yet another dimension of control that emerges naturally
from the interactions between particles and fluid in colloidal matter \cite{Brandner2019,RevModPhys.93.025008}.
Active colloidal systems show nonequilibrium self-organization with
complexity rivaling that of biological systems such as living cells,
bacterial baths, and animal flocks\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}.
A long-standing challenge in fluid mechanics
and material science is to solve the ``inverse" problem of creating a model
colloidal system that will self-assemble into a prescribed structure
\cite{PhysRevLett.128.256102}.
For example, the framework of geometrical frustration, which has been
used to explain disordered systems, could be used to design new, ordered systems
instead, through specific choices for the shapes or interactions of the particles
\cite{Manoharan2015_Science}.

The many-body hydrodynamics of amphiphilic Janus particles (JP)
assembled as vesicles and suspended
in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu20,Fu2022_JFM}.
The dynamics of the JP suspension results from the combination
of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of
a hydrophobic attraction potential (HAP).

In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of
JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane \cite{NaTr00,Fu20,KrFiGuKaHa13}.
Under background flows, the hydrodynamics of a JP vesicle (a
self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
vesicle \cite{Fu2022_JFM}: 
elongation and alignment along the extensional direction, tank-treading,
and rupture of a vesicle under shear flow.

In this work we take advantage of the flexibility of the model to examine the
effects of boundary condition on JP surfaces that could be controlled
based on the chemicals used in the experiments, for example.
It turns out that a simple tuning of the hydrophobic distribution
leads to multilamellar and striated structures. 
Here less is understood about the flow-structure interactions
and we investigate the
deformation of these novel materials in background flows
and map out their collective behavior away from equilibrium.

\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
The governing equations are a nonlinear system for the position and
orientation of a collection of rigid Janus particles. We first pose the
Stokes equations for the mobility problem giving the hydrodynamic
interactions for the particle suspension. The hydrophobic forces come
from solving a screened Laplace equation. Particle collisions are
avoided through a near-field, pair potential.

\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent.
The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
and $N_b$ is the number of particles.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
is time.  The boundary of
$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
terms are negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion.
To compute this balance, we define
the free energy\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$.
Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

@@

To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy\cite{Fu20},
we compute the variation of the domain of the free energy 
\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
and obtain 
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress.
Repulsion is rotationally symmetric and does not contribute to the torque.

Since the force and torque from the hydrodynamic stress on each particle
are in balance with the total force and torque coming from the
hydrophobic potential and repulsion, we have
\begin{equation}
  \label{eq:force}
 \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
 \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu) \, \dif s = T_i,
  \quad i=1,\ldots,N_b,
\end{equation}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor.

Once \eqref{eq:stokes}-\eqref{eq:force} have been solved,
the velocities $(\vv_i, \omega_i)$ from \eqref{eq:rigid-vel}
update the particle positions and orientations.
We use the parameters $\mu = 1$ mPa s, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
These values give a characteristic time $1$ ns and characteristic length $1$ nm.

\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
$K_0$ is the zeroth-order modified Bessel function of the first kind,
and $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation [REF]
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
$\rr = \xx - \aa_i$ [REF].

Finally, together with \eqref{eq:velocity},
\eqref{eq:stokes}-\eqref{eq:rigid-vel} become 
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:mobility}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$ [REF].

We discretize \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}
using high-order interpolation-based quadrature rules.
Integrals that are smooth are computed with
the spectrally-accurate trapezoid rule, and nearly-singular integrals,
caused by close contact between two particles, are computed with a
high-order interpolation-based quadrature rule \cite{qua-bir2014}.

After discretizing and applying quadrature,
the result is an $NN_b \times NN_b$ and $2NN_b \times 2NN_b$
linear system for \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}, respectively.
These are solved with matrix-free GMRES, and we guarantee that the number of
GMRES iterations is mesh-independent by using second-kind BIEs.

%Once the translational and angular velocities $\vv_i, \omega_i$
%have been determined, a second-order Adams-Bashforth scheme updates the particle
%positions and orientations:
%\begin{equation}
%  \label{eq:adams-bashforth}
%  \begin{aligned}
%    \aa_i(t_{n+2}) &=
%\aa_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
%    \theta_i(t_{n+2}) &=
%\theta_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
% \end{aligned}
%\end{equation}

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientations and the inset shows $N_b=60$ particles configuration.
  The particles self-assemble into distinct configurations,
  depending on the boundary condition \eqref{eq:bc-type}.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle giving bilayer structures. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
  The insest in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
  as the main panels.}
\end{caption}
\end{figure}

@@

Fig~\ref{fig:relax}(a) shows the initial configurations with
orientations of the 198-particle and 60-particle cases,
respectively. 
BC (i) with $b = 1$ mimicks an amphiphilic particle.
The boundary data $g$ is everywhere nonnegative,
and takes
the maximum value $a$ on the hydrophobic tail (red)
the value $0$ on the hydrophilic head (green). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for the 60-particle run.
Both cases form bilayers with multiple components.

@@

Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of the total particle number $(N_b)$.

@@

The vesicle shape is also tied to cell size $l$.  
Fig~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
For the smallest cell size $l = 1$ tested, the vesicle is somewhat octogonal
and passes through multiple cells (Fig~\ref{fig:BTG_Scale}(a)).
For the largest cell size $l = 4$,
the vesicle is rhomboid and surrounds a single cell.

@@

\section{Discussion}
Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
measurable structures while giving managable simulation times (days) on a single computing processor.
The simulation time for $N_b = 198$ in Fig. \ref{fig:relax} and Fig. \ref{fig:relax_energy}
was several weeks, and so we avoided simulations of this size for our results.
We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.

>>>>

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization
  is a long-standing challenging area in biology.
  To understand how hydrodynamic flow may be used to actively
  control self-assembly of Janus particles (JPs), we use a model
  recently developed for the many-body hydrodynamics of amphiphilic
  JPs suspended in a viscous background flow (JFM, 941, 2022).
  We investigate how various bilayer structures arise from tuning
  the hydrophobic properties of the JP-solvent interface.
  Focusing on a simple tuning of the hydrophobicity distribution,
  we found
  JPs assembled into uni-lamella, multi-lamella and striated
  structures.  To introduce dynamics, we include a linear shear flow and a
  Taylor-Green mixing flow, and measure the
  collective dynamics of JP particles in terms of their 
  (a) free energy from the hydrophobic interactions between the JPs,
  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
  and (c) strain parameter that captures the deformation in the assembly.
  We characterized the effective material properties of the JP structures
  and found that the uni-lamellar structures increases orientation order under
  shear flow, the multilamellar structure behaves as a shear thinning fluid,
  and the striated structure possesses a finite yield stress.  
  These numerical result provide insights into dynamic control of
  non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles (JPs) are colloids with two surfaces of different
properties. For example, it is common for the surface of a Janus
particle to be partly hydrophilic and hydrophobic (polar and non-polar).
In a viscous solvent, Janus particles often self-assemble into
structures with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
Depending on the interactions between Janus particles and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017}.

Dynamics offers yet another dimension of control that emerges naturally
from the interactions between particles and fluid in colloidal
matter~\cite{Brandner2019,RevModPhys.93.025008}. Active colloidal
systems show nonequilibrium self-organization with complexity rivaling
that of biological systems such as living cells, bacterial baths, and
animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could be used to design new, ordered systems instead, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles and suspended in a viscous fluid (at zero Reynolds number) has
been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).

In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle~\cite{Fu2022_JFM}: elongation and
alignment along the extensional direction, tank-treading, and rupture of
a vesicle under shear flow.

In this work we take advantage of the flexibility of the model to
examine the effects of boundary condition on JP surfaces that could be
controlled based on the chemicals used in the experiments, for example.
We show that a simple tuning of the hydrophobic distribution leads to
multilamellar and striated structures. Here less is understood about the
flow-structure interactions and we investigate the deformation of these
novel materials in background flows and map out their collective
behavior away from equilibrium.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
The governing equations are a nonlinear system for the position and
orientation of a collection of rigid Janus particles. We first pose the
Stokes equations for the mobility problem giving the hydrodynamic
interactions for the particle suspension. The hydrophobic forces come
from solving a screened Laplace equation. Particle collisions are
avoided through a near-field, pair potential.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent. The particles
are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \dots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free
conditions. This means that the force and torque from the hydrodynamic
stress on each particle balance the total force and torque coming from
the hydrophobic potential and repulsion. To compute this balance, we
define the free energy~\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
\begin{align}
\label{eq:free_energy}
F = \gamma
  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
\end{align}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension.

The order parameter $u(\xx,t)$ is assumed to minimize the free energy
$F$. Its governing equations $u(\xx,t)$ are a screened Laplace equation
boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

@@

To calculate the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the
free energy~\cite{Fu20}, we compute the variation of the domain of the
free energy~\eqref{eq:free_energy} subject
to~\eqref{eq:SL}--\eqref{eq:SLbc}, and obtain 
\begin{align}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{align}
for $i = 1,\dots,N_b$ with particle outward normal $\nnu$, where
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
\end{align}
is the hydrophobic stress. The repulsion is rotationally symmetric and
does not contribute to the torque.

Since the force and torque from the hydrodynamic stress on each particle
balance the total force and torque coming from the hydrophobic potential
and repulsion, we have
\begin{equation}
  \label{eq:force}
 \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
 \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu) \, \dif s = T_i,
  \quad i=1,\ldots,N_b,
\end{equation}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor.

Once \eqref{eq:stokes}--\eqref{eq:force} have been solved, the
velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
particle positions and orientations.  We use the parameters $\mu = 1$
mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
ns and characteristic length $1$ nm.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representation and time stepping}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, and $\sigma$ is
a scalar-valued density function. The subscript in $\dif s_\yy$ denotes
integration with respect to $\yy \in \Gamma$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.

We discretize~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} using high-order
interpolation-based quadrature rules.  Integrals that are smooth are
computed with the spectrally-accurate trapezoid rule, and
nearly-singular integrals, caused by close contact between two
particles, are computed with a high-order interpolation-based quadrature
rule~\cite{qua-bir2014}.

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES, and we guarantee that the
number of GMRES iterations is mesh-independent by using second-kind
BIEs.

\todo[inline]{BRYAN IS HERE}
%Once the translational and angular velocities $\vv_i, \omega_i$
%have been determined, a second-order Adams-Bashforth scheme updates the particle
%positions and orientations:
%\begin{equation}
%  \label{eq:adams-bashforth}
%  \begin{aligned}
%    \aa_i(t_{n+2}) &=
%\aa_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
%    \theta_i(t_{n+2}) &=
%\theta_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
% \end{aligned}
%\end{equation}

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientations and the inset shows $N_b=60$ particles configuration.
  The particles self-assemble into distinct configurations,
  depending on the boundary condition \eqref{eq:bc-type}.
  Panel (b) is for $b=1$ and the boundary condition mimics that
  of an amphiphilic particle giving bilayer structures. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
  The inset in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
  as the main panels.}
\end{caption}
\end{figure}

@@

Fig~\ref{fig:relax}(a) shows the initial configurations with
orientations of the 198-particle and 60-particle cases,
respectively. 
BC (i) with $b = 1$ mimics an amphiphilic particle.
The boundary data $g$ is everywhere nonnegative,
and takes
the maximum value $a$ on the hydrophobic tail (red)
the value $0$ on the hydrophilic head (green). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for the 60-particle run.
Both cases form bilayers with multiple components.

@@

Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary conditions is independent of the total particle number $(N_b)$.

@@

The vesicle shape is also tied to cell size $l$.  
Fig~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
For the smallest cell size $l = 1$ tested, the vesicle is somewhat octagonal
and passes through multiple cells (Fig~\ref{fig:BTG_Scale}(a)).
For the largest cell size $l = 4$,
the vesicle is rhomboid and surrounds a single cell.

@@

\section{Discussion}
Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
measurable structures while giving manageable simulation times (days) on a single computing processor.
The simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and Fig. \ref{fig:relax_energy}
was several weeks, and so we avoided simulations of this size for our results.
We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitatively indistinguishable
results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.
